Basic Model formulation

### 2015-02-03 documentation/interactive_spexmodel_bifurcations.Rmd
fix model definitions, local feedbacks

d_rho_1 <- function(rho, parms) { 
  with(parms,
       r * (b + (f - b) * (rho[1] - rho[2])/(1- rho[1]) ) * rho[1]^( 1 + alpha) * (1 - rho[1]/(K * (1-c*(rho[1] - rho[2])/(1- rho[1])) ) ) - m * rho[1] - ( (a + v*rho[2]/rho[1]) * rho[1]^( 1 + q) * L)/(1 +(a + v*rho[2]/rho[1]) * (h / (1- p * rho[2]/rho[1]) ) * rho[1]^( 1 + q)) 
       )  
  }

d_rho_11 <- function(rho,  parms) { 
  with(parms,
       2* (rho[1] - rho[2]) * r * (b + (f - b) * (rho[1] - rho[2])/(1- rho[1]) ) * rho[1]^( 1 + alpha) * (1 - rho[1]/(K * (1-c*(rho[1] - rho[2])/(1- rho[1])) ) ) / (1-rho[1]) - 2 * rho[2] * m  - 2 * rho[2] * ( (a + v*rho[2]/rho[1]) * rho[1]^( 1 + q) * L)/(1 +(a + v*rho[2]/rho[1]) * (h / (1- p * rho[2]/rho[1]) ) * rho[1]^( 1 + q)) 
       )  
  }

@@

@@

parms$b <- seq(0,1,.005) #seq(0,1,.002)+0.001
parms$rho_ini <- c(0.9, 0.01)

@@

plot(rho_1 ~ b, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1))

>>>>

d_rho_1 <- function(rho, parms) { 
  with(parms,
       r * (b + (1 - b) * f * (rho[1] - rho[2])/(1- rho[1]) ) * rho[1]^( 1 + alpha) * (1 - rho[1]/(K * (1-c*(rho[1] - rho[2])/(1- rho[1])) ) ) - m * rho[1] - ( (a + v*rho[2]/rho[1]) * rho[1]^( 1 + q) * L * (1 - p * rho[2]/rho[1]))/(1 +(a + v*rho[2]/rho[1]) * h  * rho[1]^( 1 + q)) 
  )  
}

d_rho_11 <- function(rho,  parms) { 
  with(parms,
       2* (rho[1] - rho[2]) * r * (b + (1 - b) * f * (rho[1] - rho[2])/(1- rho[1]) ) * rho[1]^( 1 + alpha) * (1 - rho[1]/(K * (1-c*(rho[1] - rho[2])/(1- rho[1])) ) ) / (1-rho[1]) - 2 * rho[2] * m  - 2 * rho[2] * ( (a + v*rho[2]/rho[1]) * rho[1]^( 1 + q) * L * (1 - p * rho[2]/rho[1]))/(1 +(a + v*rho[2]/rho[1]) * h  * rho[1]^( 1 + q)) 
  )  
}

@@

inputPanel(
  selectInput("gradient", label = "select gradient:",             choices = c("b", "L"), selected = "b")
  )

@@

 if(input$gradient == "b") parms$b <- seq(0,1,.005) 
 if(input$gradient == "L") parms$L <- seq(0,20,.1)

parms$rho_ini <- c(0.9, 0.01)

@@

 if(input$gradient == "b") plot(rho_1 ~ b, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1))
 if(input$gradient == "L") plot(rho_1 ~ L, data = cbind(output, iterations), type = "p", pch  = 20, ylim = c(0,1))

### 2015-02-03 documentation/model_formulation.Rmd
bugfix bifurcation over L
fix model definitions, local feedbacks

$$ \frac{dV}{dt} = G(V) - C(V)g $$

with growth function $G$ and a function $C$ which represents consumption by a herbivore multiplied by the density of herbivores, the livestock rate, $g$. Formally, intrinsic mortality could be included in both terms. In the formulations of @noy-meir75 and @vandekoppel97 it is assumed to be covered by the logistic growth function.

@@

defplot <- function(...) plot(..., 
            type = "l", 
            bty = "l", cex = 0.7, las = 1,
            xlim = c(0,1), ylim = c(0,1), 
            xaxs = "i", yaxs = "i", 
            xaxp = c(0,1,2), yaxp = c(0,1,2), 
            xlab = "vegetation cover")

@@

G <- function(P, r = 2, K = 1) r*P*(1-P/K)

@@

r <- function(P, r_0 =  2.25, a = 1) r_0 *P^a

@@

G_sig <- function(P, r_0 = 2.25, a = 1,  K = 0.9) r(P, r_0, a)*P*(1-P/K)

defplot(rho, G_sig(rho), ylab = "growth")
lines(rho, G_sig(rho, a = 0))
lines(rho, G_sig(rho,r_0 = 2.25, a = 1))
lines(rho, G_sig(rho,r_0 = 2.25, a = 0.2))
```

@@

```{r, echo=FALSE}
C <- function(V, L = 10, g = 0.01) (g*V*L)

@@

```{r, echo=FALSE}
C <- function(V, L = 10, g = 0.01) g * L + V*0

@@

```{r, echo=FALSE}
C <- function(V, L = 10, a = 0.6, h = 100) (a*V*L)/(1+a*h*V)

@@

```{r, echo=FALSE}
C <- function(V, L = 10, a = 0.6, h = 100, q = 1) (a*V^(1+q)*L)/(1+a*h*(V^(1+q)) )

@@

C <- function(V, m_0 = 0.05, L = 10, a = 0.6, h = 100, q = 0) (m_0 * V) +(a*V^(1+q)*L)/(1+a*h*(V^(1+q)) )

@@

defplot(rho, G(rho), ylab = "growth", col = "green3")
lines(rho, C(rho, L = 10, a = 0.01, h = 0.00001))
lines(rho, C(rho, L = 25, a = 0.01, h = 0.00001))
lines(rho, C(rho, L = 50, a = 0.01, h = 0.00001))
abline( h = 0.1 )
abline( h = 0.25 )
abline( h = 0.5 )
```

@@

defplot(rho, G(rho), ylab = "growth", col = "green3")
lines(rho, C(rho, L = 10))
lines(rho, C(rho, L = 25))
lines(rho, C(rho, L = 50))

@@

defplot(rho, G(rho), ylab = "growth", col = "green3")
lines(rho, C(rho, L = 10, q = 1))
lines(rho, C(rho, L = 25, q = 1))
lines(rho, C(rho, L = 50, q = 1))

@@

parms <- list(
    m = 0.05,
    r = 1,
    b = 0.9, 
    K = 0.9, 
    a = 0.6,
    h = 100,
    L = 10
  )

@@

parms <- list(
    m = 0.05,
    r = 1,
    b = 0.9, 
    K = 0.9, 
    a = 0.6,
    h = 100,
    L = 10, 
    alpha = 0,
    q = 0
  )

@@

@@

$$ b = b^* + (f - b^*) q_{0|1} \,,$$

@@

@@

@@

@@

An alternative formulation should be found. The term is highly non-linear and provokes relevant changes only at values above 0.9. It is defined within $(0,1($

@@

$$ w_{1,0} = m + ( a^*  + v q_{1|1})L\rho_1^{q}{1+( a^*  + v q_{1|1})(h^*/ (1 - p  q_{1|1}))\rho_1^{1+q}} $$

$$ w_{0,1} = \frac{r \rho_1^{1+\alpha} (b^* + (f - b^*) q_{0|1}) (1-\frac{\rho_1}{K^* (1 - c q_{0|1})})}{1-\rho_1} $$

@@

@@

$$  \frac{\mathrm{d}\rho_11}{\mathrm{d}t} = 2 \rho_{10} \frac{r \rho_1^{1+\alpha} (b^* + (f - b^*) q_{0|1}) (1-\frac{\rho_1}{K^* (1 - c q_{0|1})})}{1-\rho_1} - 2 \rho_{11} m -  2 \rho_{11} \frac{(a^*  + v q_{1|1})L\rho_1^{q}}{1+(a^*  + v q_{1|1})(h^*  / (1 - p  q_{1|1}))\rho_1^{1+q}}  $$

$$  \frac{\mathrm{d}\rho_{1}}{\mathrm{d}t} = \rho_{0}\frac{r \rho_1^{1+\alpha} (b^* + (f - b^*) q_{0|1}) (1-\frac{\rho_1}{K^* (1 - c q_{0|1})})}{1-\rho_1} - \rho_{1}m - \frac{(a^*  + v q_{1|1})L\rho_1^{1+q}}{1+(a^*  + v q_{1|1})(h^*  / (1 - p  q_{1|1}))\rho_1^{1+q}}   $$

@@

$$  \frac{\mathrm{d}\rho_11}{\mathrm{d}t} = 2 \rho_{10} \frac{r \rho_1^{1+\alpha} (b^* + (f - b^*) q_{0|1}) (1-\frac{\rho_1}{K^* (1 - c q_{0|1})})}{1-\rho_1} - 2 \rho_{11} m -  2 \rho_{11} \frac{(a^*  + v q_{1|1})L\rho_1^{q}}{1+(a^*  + v q_{1|1})(h^*  / (1 - p  q_{1|1}))\rho_1^{1+q}}  $$

$$  \frac{\mathrm{d}\rho_{1}}{\mathrm{d}t} = r \rho_1^{1+\alpha} (b^* + (f - b^*) q_{0|1}) (1-\frac{\rho_1}{K^* (1 - c q_{0|1})}) - \rho_{1}m - \frac{(a^*  + v q_{1|1})L\rho_1^{1+q}}{1+(a^*  + v q_{1|1})(h^*  / (1 - p  q_{1|1}))\rho_1^{1+q}}   $$

@@

$$  \frac{\mathrm{d}\rho_{11} }{\mathrm{d}t} = 2 (\rho_1 - \rho_{11}) \frac{r \rho_1^{1+\alpha} (b^* + (f - b^*) \frac{\rho_{1} - \rho_{11}}{1 - \rho_1}) (1-\frac{\rho_1}{K^* (1 - c \frac{\rho_{1} - \rho_{11}}{1 - \rho_1})})}{1-\rho_1} - 2 \rho_{11} m -  2 \rho_{11} \frac{(a^*  + v \frac{\rho_{11}}{\rho_1})L\rho_1^{q}}{1+(a^*  + v \frac{\rho_{11}}{\rho_1})(h^*  / (1 - p  \frac{\rho_{11}}{\rho_1}))\rho_1^{1+q}}  $$

$$  \frac{\mathrm{d}\rho_{1}}{\mathrm{d}t} = r \rho_1^{1+\alpha} (b^* + (f - b^*) \frac{\rho_{1} - \rho_{11}}{1 - \rho_1}) (1-\frac{\rho_1}{K^* (1 - c \frac{\rho_{1} - \rho_{11}}{1 - \rho_1})}) - \rho_{1}m -  \frac{(a^*  + v \frac{\rho_{11}}{\rho_1})L\rho_1^{1+q}}{1+(a^*  + v \frac{\rho_{11}}{\rho_1})(h^*  / (1 - p  \frac{\rho_{11}}{\rho_1}))\rho_1^{1+q}}   $$

Thus, we can solve the ODE for a given set of parameters

we get the following dynamics

@@

d_rho_1 <- function(rho, parms) { 
  with(parms,
       r * (b + (f - b) * (rho[1] - rho[2])/(1- rho[1]) ) * rho[1]^( 1 + alpha) * (1 - rho[1]/(K * (1-c*(rho[1] - rho[2])/(1- rho[1])) ) ) - m * rho[1] - ( (a + v*rho[2]/rho[1]) * rho[1]^( 1 + q) * L)/(1 +(a + v*rho[2]/rho[1]) * (h / (1- p * rho[2]/rho[1]) ) * rho[1]^( 1 + q)) 
       )  
  }

d_rho_11 <- function(rho,  parms) { 
  with(parms,
       2* (rho[1] - rho[2]) * r * (b + (f - b) * (rho[1] - rho[2])/(1- rho[1]) ) * rho[1]^( 1 + alpha) * (1 - rho[1]/(K * (1-c*(rho[1] - rho[2])/(1- rho[1])) ) ) / (1-rho[1]) - 2 * rho[2] * m  - 2 * rho[2] * ( (a + v*rho[2]/rho[1]) * rho[1]^( 1 + q) * L)/(1 +(a + v*rho[2]/rho[1]) * (h / (1- p * rho[2]/rho[1]) ) * rho[1]^( 1 + q)) 
       )  
  }

@@

@@

parms$L <- seq(0,20,0.2) #seq(0,1,.002)+0.001
parms$rho_ini <- c(0.9, 0.01)

@@

>>>>

$$ \frac{dV}{dt} = G(V) - C(V)L $$

with growth function $G$ and a function $C$ which represents consumption by a herbivore multiplied by the density of herbivores, the livestock rate, $L$. Formally, intrinsic mortality could be included in both terms. In the formulations of @noy-meir75 and @vandekoppel97 it is assumed to be covered by the logistic growth function.

@@

defplot <- function(...) plot(..., 
            type = "l", 
            bty = "l", cex = 0.7, las = 1,
            xlim = c(0,1), ylim = c(0,0.4), 
            xaxs = "i", yaxs = "i", 
            xaxp = c(0,1,2), yaxp = c(0,1,2), 
            xlab = "vegetation cover")

@@

G <- function(P, r = 1, K = 1) r*P*(1-P/K)

@@

r <- function(P, r_0 =  1, a = 1) r_0 *P^a

@@

G_sig <- function(P, r_0 = 1, a = 1,  K = 0.9) r(P, r_0, a)*P*(1-P/K)

defplot(rho, G_sig(rho), ylab = "growth")
lines(rho, G_sig(rho, a = 0))
lines(rho, G_sig(rho, a = 1))
lines(rho, G_sig(rho, a = 0.2))
```

@@

```{r, echo=FALSE}
C <- function(V, L = 5, g = 0.01) (g*V*L)

@@

```{r, echo=FALSE}
C <- function(V, L = 5, g = 0.01) g * L + V*0

@@

```{r, echo=FALSE}
C <- function(V, L = 5, a = 0.6, h = 100) (a*V*L)/(1+a*h*V)

@@

```{r, echo=FALSE}
C <- function(V, L = 5, a = 0.6, h = 100, q = 1) (a*V^(1+q)*L)/(1+a*h*(V^(1+q)) )

@@

C <- function(V, m_0 = 0.05, L = 5, a = 0.6, h = 100, q = 0) (m_0 * V) +(a*V^(1+q)*L)/(1+a*h*(V^(1+q)) )

@@

defplot(rho, G(rho), ylab = "growth", col = "green3")
lines(rho, C(rho, L = 10, a = 0.01, h = 0.00001))
lines(rho, C(rho, L = 25, a = 0.01, h = 0.00001))
lines(rho, C(rho, L = 50, a = 0.01, h = 0.00001))
abline( h = 0.1 )
abline( h = 0.25 )
```

@@

defplot(rho, G(rho), ylab = "growth", col = "green3")
lines(rho, C(rho, L = 5))
lines(rho, C(rho, L = 10))
lines(rho, C(rho, L = 25))

@@

defplot(rho, G(rho), ylab = "growth", col = "green3")
lines(rho, C(rho, L = 5, q = 1))
lines(rho, C(rho, L = 10, q = 1))
lines(rho, C(rho, L = 25, q = 1))

@@

parms <- list(
    m = 0.05,
    r = 1,
    b = 0.9, 
    K = 0.9, 
    a = 0.6,
    h = 100,
    L = 5
  )

@@

parms <- list(
    m = 0.05,
    r = 1,
    b = 0.9, 
    K = 0.9, 
    a = 0.6,
    h = 100,
    L = 5, 
    alpha = 0,
    q = 0,
    c = 0,
    f = 0,
    v = 0,
    p = 0
  )

@@

parms <- list(
    m = 0.05,
    r = 1,
    b = 0.9, 
    K = 0.9, 
    a = 0.6,
    h = 100,
    L = 16, 
    alpha = 0.1,
    q = 1,
    c = 0,
    f = 0,
    v = 0,
    p = 0

  )

@@

$$ b = b^* + (1 - b^*)  f q_{0|1} \,,$$

@@

G <- function(V, q_01 = "auto", r_0 = 1, b = 0.1, f = 0, alpha = 0,  K = 0.9, c = 0) {
  if(q_01 == "auto") q_01 <- 1
  r_0*(b + (1-b)*f*q_01)*V^(1+alpha)*(1-V/(K * (1-c * q_01) ) )

}

defplot(rho, G(rho, 1, f = 0.8), ylab = "growth", col = "green3")
lines(rho,G(rho, 0.75, f = 0.8), col = "green3")
lines(rho,G(rho, 0.5, f = 0.8), col = "green3")
lines(rho,G(rho, 0.25, f = 0.8), col = "green3")
lines(rho,G(rho, 0, f = 0.8), col = "green3")

lines(rho, C(rho, L = 10))

@@

defplot(rho, G(rho, 1, c = 0.3, b = 0.9), ylab = "growth", col = "green3")
lines(rho,G(rho, 0.75, c = 0.3, b = 0.9), col = "green3")
lines(rho,G(rho, 0.5, c = 0.3, b = 0.9), col = "green3")
lines(rho,G(rho, 0.25, c = 0.3, b = 0.9), col = "green3")
lines(rho,G(rho, 0, c = 0.3, b = 0.9), col = "green3")

lines(rho, C(rho, L = 10))

@@

C <- function(V, q_01 = 1, m_0 = 0.05, L = 5, a = 0.1, h = 100, q = 0, p = 0, v = 0) (m_0 * V) +( (a+v*q_01  ) *V^(1+q)*L*(1-p*q_01))/(1+(a+v*q_01)*h*(V^(1+q)) )

defplot(rho, C(rho, 1, v = 0.5), ylab = "mortality")
lines(rho,C(rho, 0.75, v = 0.5))
lines(rho,C(rho, 0.5, v = 0.5))
lines(rho,C(rho, 0.25, v = 0.5))
lines(rho,C(rho, 0, v = 0.5))

lines(rho, G(rho, b = 0.6), col = "green3")

@@

An alternative formulation should be found. The term is highly non-linear and provokes relevant changes only at values above 0.9. It is defined within $(0,1($ 
Instead, we could define associational protection as a reduced impact due to a reduced local density of grazers.

$$ L = L^* (1 - p  q_{1|1}) $$

defplot(rho, C(rho, 1, p = 0.8, L = 10), ylab = "mortality")
lines(rho,C(rho, 0.75, p = 0.8, L = 10))
lines(rho,C(rho, 0.5, p = 0.8, L = 10))
lines(rho,C(rho, 0.25, p = 0.8, L = 10))
lines(rho,C(rho, 0, p = 0.8, L = 10))

lines(rho, G(rho, b = 0.6), col = "green3")

#### multiple effects

If those effects coincide, potentially even with the global feedbacks, the intersections are difficult to estimate.

defplot(rho, C(rho, 1, p = 0.8, v = 0.6, L = 10, q = .5), ylab = "mortality")
lines(rho,C(rho, 0.75, p = 0.8, v = 0.6, L = 10, q = .5))
lines(rho,C(rho, 0.5, p = 0.8,v = 0.6,  L = 10, q = .5))
lines(rho,C(rho, 0.25, p = 0.8,v = 0.6,  L = 10, q = .5))
lines(rho,C(rho, 0, p = 0.8,v = 0.6,  L = 10, q = .5))

lines(rho, G(rho, 1, c = 0.3, f = 0.9, b = 0.3, alpha = 0.5), col = "green3")
lines(rho,G(rho, 0.75, c = 0.3,f = 0.9,  b = 0.3, alpha = 0.5), col = "green3")
lines(rho,G(rho, 0.5, c = 0.3,f = 0.9,  b = 0.3, alpha = 0.5), col = "green3")
lines(rho,G(rho, 0.25, c = 0.3, f = 0.9, b = 0.3, alpha = 0.5), col = "green3")
lines(rho,G(rho, 0, c = 0.3,f = 0.9,  b = 0.3, alpha = 0.5), col = "green3")

@@

$$ w_{1,0} = m + ( a^* + v q_{1|1})L^* (1 - p  q_{1|1})\rho_1^{q}{1+( a^*  + v q_{1|1})h\rho_1^{1+q}} $$

$$ w_{0,1} = \frac{r \rho_1^{1+\alpha} (b^* + (1 - b^*) f q_{0|1}) (1-\frac{\rho_1}{K^* (1 - c q_{0|1})})}{1-\rho_1} $$

@@

Thus, we can run the CA for a given set of parameters

set.seed(565432) # setting seed for random number generation

spexmodel <- runCA(0.9, parms, delta = 0.2, t_max = 150, t_min = 100, t_eval = 50, isstable = 0.0001, saveeach = 1)

plot(spexmodel$rho_one ~ spexmodel$time, 
     ylim = c(0,1), ylab = expression( rho["+"]), 
     xlab = "time [yr]", type = "l")

@@

$$  \frac{\mathrm{d}\rho_{11}}{\mathrm{d}t} = 2 \rho_{10} \frac{r \rho_1^{1+\alpha} (b^* + (1 - b) f q_{0|1})) (1-\frac{\rho_1}{K^* (1 - c q_{0|1})})}{1-\rho_1} - 2 \rho_{11} m -  2 \rho_{11} \frac{(a^*  + v q_{1|1})L^* (1 - p  q_{1|1})\rho_1^{q}}{1+(a^*  + v q_{1|1})h\rho_1^{1+q}}  $$

$$  \frac{\mathrm{d}\rho_{1}}{\mathrm{d}t} = \rho_{0}\frac{r \rho_1^{1+\alpha} (b^* + (1 - b)  f q_{0|1})) (1-\frac{\rho_1}{K^* (1 - c q_{0|1})})}{1-\rho_1} - \rho_{1}m - \frac{(a^*  + v q_{1|1})L^* (1 - p  q_{1|1})\rho_1^{1+q}}{1+(a^*  + v q_{1|1})h\rho_1^{1+q}}   $$

@@

$$  \frac{\mathrm{d}\rho_{11}}{\mathrm{d}t} = 2 \rho_{10} \frac{r \rho_1^{1+\alpha} (b^* + (1 - b)  f q_{0|1})) (1-\frac{\rho_1}{K^* (1 - c q_{0|1})})}{1-\rho_1} - 2 \rho_{11} m -  2 \rho_{11} \frac{(a^*  + v q_{1|1})L^* (1 - p  q_{1|1}) \rho_1^{q}}{1+(a^*  + v q_{1|1})h)\rho_1^{1+q}}  $$

$$  \frac{\mathrm{d}\rho_{1}}{\mathrm{d}t} = r \rho_1^{1+\alpha} (b^* + (1 - b)  f q_{0|1})) (1-\frac{\rho_1}{K^* (1 - c q_{0|1})}) - \rho_{1}m - \frac{(a^*  + v q_{1|1})L^* (1 - p  q_{1|1})\rho_1^{1+q}}{1+(a^*  + v q_{1|1})h\rho_1^{1+q}}   $$

@@

$$  \frac{\mathrm{d}\rho_{11} }{\mathrm{d}t} = 2 (\rho_1 - \rho_{11}) \frac{r \rho_1^{1+\alpha} (b^* + (1 - b)  f \frac{\rho_{1} - \rho_{11}}{1 - \rho_1} )) (1-\frac{\rho_1}{K^* (1 - c \frac{\rho_{1} - \rho_{11}}{1 - \rho_1})})}{1-\rho_1} - 2 \rho_{11} m -  2 \rho_{11} \frac{(a^*  + v \frac{\rho_{11}}{\rho_1})L^* (1 - p \frac{\rho_{11}}{\rho_1})\rho_1^{q}}{1+(a^*  + v \frac{\rho_{11}}{\rho_1})h\rho_1^{1+q}}  $$

$$  \frac{\mathrm{d}\rho_{1}}{\mathrm{d}t} = r \rho_1^{1+\alpha} (b^* + (1 - b) f  \frac{\rho_{1} - \rho_{11}}{1 - \rho_1}) (1-\frac{\rho_1}{K^* (1 - c \frac{\rho_{1} - \rho_{11}}{1 - \rho_1})}) - \rho_{1}m -  \frac{(a^*  + v \frac{\rho_{11}}{\rho_1})L^* (1 - p \frac{\rho_{11}}{\rho_1})\rho_1^{1+q}}{1+(a^*  + v \frac{\rho_{11}}{\rho_1})h\rho_1^{1+q}}   $$

for the set of parameters given above, we get the following dynamics

@@

d_rho_1 <- function(rho, parms) { 
  with(parms,
       r * (b + (1 - b) * f * (rho[1] - rho[2])/(1- rho[1]) ) * rho[1]^( 1 + alpha) * (1 - rho[1]/(K * (1-c*(rho[1] - rho[2])/(1- rho[1])) ) ) - m * rho[1] - ( (a + v*rho[2]/rho[1]) * rho[1]^( 1 + q) * L * (1 - p * rho[2]/rho[1]))/(1 +(a + v*rho[2]/rho[1]) * h  * rho[1]^( 1 + q)) 
       )  
  }

d_rho_11 <- function(rho,  parms) { 
  with(parms,
       2* (rho[1] - rho[2]) * r * ( b + (1 - b) * f * (rho[1] - rho[2])/(1- rho[1]) ) * rho[1]^( 1 + alpha) * (1 - rho[1]/(K * (1-c*(rho[1] - rho[2])/(1- rho[1])) ) ) / (1-rho[1]) - 2 * rho[2] * m  - 2 * rho[2] * ( (a + v*rho[2]/rho[1]) * rho[1]^( 1 + q) * L * (1 - p * rho[2]/rho[1]))/(1 +(a + v*rho[2]/rho[1]) * h  * rho[1]^( 1 + q)) 
       )  
  }

@@

lines(spexmodel$rho_one ~ spexmodel$time, col = "grey50")

@@

parms$L <- seq(0,20,0.2) #seq(0,1,.002)+0.001
parms$b <- 0.4
parms$rho_ini <- c(0.9, 0.01)

@@

## analytical solutions
